Legacy Data Confounds Genomics Studies

### 2019-02-21 legacy.tex
minor edits

Different mutagenic processes may preferentially affect different DNA motifs. 
Certain mutagens in tobacco smoke, for example, have been shown to preferentially bind to certain genomic motifs leading to an excess of G to T transversions \citep{Pfeifer2002,Pleasance2010}. 
Thus, exposure of populations to different mutational processes can be inferred by considering the DNA context of polymorphism in search of \textit{signatures} of different mutational processes \citep{Alexandrov2013,Shiraishi2015a}. 
Such genome-wide mutational signatures have been used as diagnostic tools for cancers \citep{Alexandrov2013,Shiraishi2015a}.

>>>>

Different mutagenic processes may preferentially affect different DNA motifs. 
Certain mutagens in tobacco smoke, for example, have been shown to preferentially bind to certain genomic motifs leading to an excess of G to T transversions \citep{Pfeifer2002,Pleasance2010}. 
Thus, the impact of mutational processes can be inferred by considering the DNA context of a polymorphism \citep{Alexandrov2013,Shiraishi2015a}. 
%Thus, exposure of populations to different mutational processes can be inferred by considering the DNA context of polymorphism in search of \textit{signatures} of different mutational processes \citep{Alexandrov2013,Shiraishi2015a}. 
Such genome-wide mutational signatures have been used as diagnostic tools for cancers \citep{Alexandrov2013,Shiraishi2015a}.
